Bootstrap Confidence Intervals for Sharp Regression Discontinuity Designs

### 2016-08-12 main_paper.tex
First batch of tweaks for section on simulations.

\section{Simulation Evidence}\label{sim}
This section presents evidence from Monte Carlo simulations that the bootstrap
procedures proposed in Section~\ref{boot} produce valid, robust confidence
intervals similar to those obtained by the analytical procedures established
in CCT. The bootstrap CIs obtained are comparable to the analytical
alternative, albeit with slightly lower coverage and shorter
length of the intervals in the specifications implemented. We also find that
all of the bias corrected methods can offer substantial improvements over
estimators that do not bias correct.

The Monte Carlo experiments have a similar structure. For all of them, we
generate 500 i.i.d.\ observations from the DGP
\begin{align*}
Y_{i}           &= \mu_{j}(X_{i}) + \varepsilon_{i} \\
X_{i}           &\sim  2 \times \betarv(2,4) - 1 \\
\varepsilon_{i} &\sim N(0, 0.1295^2 \times \sigma_i^2) \\
\sigma_i &= z(\gamma) \mu_{j}(X_{i})^\gamma ,
\end{align*}
where $j$ indexes the specific DGP and $z(\gamma)$ is a scale parameter that
ensures that the average variance in a neighborhood around the cutoff
equals the unconditional value under homoskedasticity; i.e. $z(\gamma)$
satisfies
\[
  z(\gamma)^2
    = \frac{1}{\sum_{i = 1}^n \mu_{j}(X_{i})^{2 \gamma}
    \frac{\1\{\min(-\bar h, -\bar b) \leq X_i \leq \max(\bar h,\bar b)\}}
    {\#\{X_i : \min(-\bar h, -\bar b) \leq X_i \leq \max(\bar h, \bar b)\}}};
\]
for $\gamma = 0$ we have $z(\gamma) = 1$ and the errors are
homoskedastic.\footnote{%
  The values $\bar h$ and $\bar b$ are taken as the average values over 500
  homoskedastic simulations of the bandwidths returned by CCT's optimal
  bandwidth selector. This ensures that the relevant variance around the cutoff
  is approximately the same for the heteroskedastic and homoskedastic DGPs.} %
This is the experimental design used by \citet{IK} and CCT for homoskedastic
simulations, which we adopt here to make our simulation results directly
comparable with theirs and with the rest of the literature.  The form of
heteroskedasticity is motivated by \cite{mackinnon2013thirty}, and we consider
$\gamma$ equal to 0 and 2 for the simulations.
We use the same three functional forms for $\mu_{j}$ as CCT.

@@

\nocite{ludwig2007}%
The second DGP is based on Ludwig and Miller's (2007) analysis of the Head Start
program. Funding eligibility is determined at the county level using the
county's historical poverty rate, with a sharp threshold that determines the
provision of services. We use the fifth order polynomial estimated on Ludwig and
Miller's dataset as the conditional expectation for the second DGP:
\begin{equation*}
  \mu_{2}(x) =
  \begin{cases}
    3.71 + 2.30x + 3.28x^2 + 1.45x^3 + 0.23x^4 + 0.03x^5
    & \textif\ x < 0, \\
    0.26 + 18.49x - 54.81x^2 + 74.30x^3 - 45.02x^4 + 9.83x^5
    & \otherwise
  \end{cases}
\end{equation*}
and the population ATE is $-3.45$ $(= 0.26 - 3.71)$.

>>>>

\section{Simulation Evidence}\label{sim}
This section presents evidence from Monte Carlo simulations that the bootstrap
procedures proposed in Section~\ref{boot} produce valid, robust confidence
intervals (CIs) similar to those obtained by the analytical procedures established in CCT. 
The CIs obtained are comparable to the analytical alternative, and in many cases provide
 coverage closer to the nominal size of the tests in the specifications implemented.
 We also observe that all of the bias corrected methods can offer substantial improvements over estimators that do not bias correct.

The Monte Carlo experiments have a similar structure. For all of them, we generate 500 i.i.d.\ observations from the DGP
\begin{align*}
Y_{i}           &= \mu_{j}(X_{i}) + \varepsilon_{i} \\
X_{i}           &\sim  2 \times \betarv(2,4) - 1 \\
\varepsilon_{i} &\sim N(0, 0.1295^2 \times \sigma_i^2) \\
\sigma_i &= z(\gamma) \mu_{j}(X_{i})^\gamma ,
\end{align*}
where $j$ indexes the specific DGP and $z(\gamma)$ is a scale parameter that
ensures that the average variance in a neighborhood around the cutoff
equals the unconditional value under homoskedasticity; i.e. $z(\gamma)$
satisfies
\[
  z(\gamma)^2
    = \frac{1}{\sum_{i = 1}^n \mu_{j}(X_{i})^{2 \gamma}
    \frac{\1\{\min(-\bar h, -\bar b) \leq X_i \leq \max(\bar h,\bar b)\}}
    {\#\{X_i : \min(-\bar h, -\bar b) \leq X_i \leq \max(\bar h, \bar b)\}}};
\]
for $\gamma = 0$ we have $z(\gamma) = 1$ and the errors are
homoskedastic.\footnote{%
  The values $\bar h$ and $\bar b$ are taken as the average values over 500
  homoskedastic simulations of the bandwidths returned by CCT's optimal
  bandwidth selector. This ensures that the relevant variance around the cutoff
  is approximately the same for the heteroskedastic and homoskedastic DGPs.} %
This is the experimental design used by \citet{IK} and CCT for homoskedastic
simulations, which we adopt here to make our simulation results directly
comparable with theirs and with the rest of the literature.  The form of
heteroskedasticity is motivated by \cite{mackinnon2013thirty}. Hence,
 we consider both homoskedastic and heteroskedastic cases by setting $\gamma$ equal to 0 and 2 for the simulations, respectively.
We use the same three functional forms for $\mu_{j}$ as CCT.

@@

\nocite{ludwig2007}%
The second DGP is based on Ludwig and Miller's (2007) analysis of the Head Start program.
As described in Section \ref{application}, eligibility to grant-writing assistance is determined
 at the county level using the county's historical poverty rate, with a sharp threshold that
 determines the provision of services. We use the fifth order polynomial estimated on Ludwig
 and Miller's dataset as the conditional expectation for the second DGP:
\begin{equation*}
  \mu_{2}(x) =
  \begin{cases}
    3.71 + 2.30x + 3.28x^2 + 1.45x^3 + 0.23x^4 + 0.03x^5
    & \textif\ x < 0, \\
    0.26 + 18.49x - 54.81x^2 + 74.30x^3 - 45.02x^4 + 9.83x^5
    & \otherwise
  \end{cases}
\end{equation*}
and the population ATE is $-3.45$ $(= 0.26 - 3.71)$.
